\documentclass[11pt]{article}
\usepackage{cosai}

\title{Add CoSAI Full Paper Title Here}
\author{Workstream Name}

\begin{document}

% --- Front Cover ---
\makeCoSAICover{ADD TITLE HERE}{Workstream Name}

% --- Table of Contents ---
\newpage
\tableofcontents

% --- Abstract Page ---
\newpage
\section*{Abstract}
\begin{center}
    \begin{tabular}{ccc}
        \sectionIcon{a}{Practical}{Cooperation} & 
        \sectionIcon{b}{MCP}{Security} & 
        \sectionIcon{c}{Actionable}{Controls}
    \end{tabular}
\end{center}

\vspace{1cm}
Summary of the technical purpose of the document. By creating structured opportunities for interaction and feedback, it aims to foster cooperation and produce outcomes that are practical, measurable, and valued by all involved.

% --- Introduction (Dark Background Section) ---
\newpage
\pagecolor{cosaiDarkBlue}\color{white}
\section*{\color{white}Introduction}
Since its emergence a year ago, MCP has rapidly established itself as the protocol for transmitting structured context between AI agents and services. Given the growing importance and attack surface of MCP and agentic systems, it is imperative that deployment specific security threats are identified.

% --- Technical Section ---
\newpage
\pagecolor{white}\color{black}
\section{MCP Architecture and Standards}
MCP is an open standard developed by Anthropic and a growing open source community that provides a structured framework for connecting large language models and AI agents to external tools, data sources, and services.

\subsection{Client-Server Architecture}
MCP follows a client-server architecture where host applications (such as AI assistants, IDEs, or workflow automation tools) use MCP clients to connect to local or remote MCP servers.

\begin{itemize}
    \item{} \textbf{Discovery:} Standardized methods for discovering available capabilities.
    \item{} \textbf{Invocation:} Invoking parametrized services.
    \item{} \textbf{Transport:} Supports stdio for local and Streamable HTTP for remote.
\end{itemize}

% --- Conclusions ---
\section{Takeaways and Conclusion}
Organizations deploying MCP-based systems must develop defense-in-depth strategies including zero-trust architectures and hardware-based isolation through trusted execution environments.

% --- Acknowledgements ---
\newpage
\section*{Acknowledgements}
\textbf{Workstream Leads}
\begin{itemize}
    \item{} Sarah Novotny
    \item{} Ian Molloy, IBM
    \item{} Raghu Yeluri, Intel
\end{itemize}

\end{document}